term papaer 2

### 2024-02-13 outputs/paper/paper.qmd
paper

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
install.packages("here")
install.packages("dplyr") 
install.packages("tidyr") 
install.packages("tidyverse")
installed.packages("ggplot2")
install.packages("kableExtra") 
# install.packages("knitr")

library(here)
library(dplyr)
library(tidyverse)
library(knitr)
library(rdrobust)
library(ggplot2)
library(tidyr) 
library(kableExtra)

@@

ggplot(data_long, aes(x=Value, fill=Variable)) + 
  geom_histogram(position="dodge", binwidth=1) + 
  facet_wrap(~ Variable, scales = "free_x") + 
  theme_minimal() + 
  ggtitle("hist") +
  xlab("Value") +
  ylab("Frequency") +
  scale_fill_manual(values = c("inc_0_50_post" = "blue", "inc_post" = "red", "unempl_post" = "green"))
```

```{r}
#| label: fig-hist
#| tbl-cap: histogram
#| echo: false
#| message: false
#| warning: false

>>>>

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
install.packages("here")
install.packages("dplyr") 
install.packages("tidyverse")
installed.packages("ggplot2")
# install.packages("knitr")

library(here)
library(dplyr)
library(tidyverse)

library(ggplot2)

@@

ggplot(data_long, aes(x=Value, fill=Variable)) + 
  geom_histogram(position="dodge", binwidth=1) + 
  facet_wrap(~ Variable, scales = "free_x") + 
  theme_minimal() + 
  ggtitle("hist") +
  xlab("Value") +
  ylab("Frequency") +
  scale_fill_manual(values = c("inc_0_50_post" = "blue", "inc_post" = "red", "unempl_post" = "green"))
